\documentclass[a4paper,10pt]{tufte-book}

\usepackage{listings}
\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{moreverb}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{float}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage[toc,page]{appendix}

\usepackage{titlesec}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage{tikz}\usetikzlibrary{shapes.misc}
\newcommand\qnhead{\vspace{0.25cm}%
\tikz[baseline,trim left=3.1cm, trim right=3cm] {
        \fill [black!12] (2.5cm,-1ex) rectangle (\textwidth+3.3cm,2.5ex);
        \node [
            anchor= base east,
            rectangle,
            minimum height=3.5ex] at (3cm,0ex) {
    \thesection
};
}\vspace{0.25cm}}
\renewcommand{\thesection}{}

\title{SparQLed\\
{\normalsize --- Assisted SPARQL Editor through RDF Graph Analytics}}

\begin{document}

\maketitle

\newthought{SparQLed is an interactive SPARQL editor} that helps users in formulating complex SPARQL queries across multiple heterogeneous data sources. Whether or not the structure and vocabulary of data sources are known, users can easily formulate queries through various kinds of context-aware element recommendations.

This document presents the steps to setup the editor:
\begin{enumerate}
\item Compute the Data Graph Summary;
\item Configure the webapp;
\item Launch the SparQLed webapp.
\end{enumerate}

\input{dgs}
\input{start}
\input{dgs-compute}
\input{webapp}
\input{sparqled}

\qnhead{KNOWN ISSUES}

The editor use the SPARQL1.0 grammar. Therefore, there is no syntax highlighting nor syntax recommendations\footnote{\textcolor{blue}{not to be confused with the structural recommendations the SparQLed provides}} for SPARQL1.1 keywords. However, it is still possible to submit a 1.1 query to the endpoint. This issue will be resolved in the near future.

\qnhead{ACKNOWLEDGEMENT}

This software is based upon works supported by the European FP7 project LOD2 (257943).

\qnhead{CONTACT}

If you have any questions or issues, please contact us at \url{http://groups.google.com/group/sindice-dev}.

\bibliography{sparqled-doc}
\bibliographystyle{plainnat}

\input{appendix}

\end{document}
